---
title: "simulations"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE)


```

```{r}
library(targets)
library(tidyverse)
library(glue)
library(gt)
library(googlesheets4)



# ugh whyeee
source("R/hpp_themes.R")


```


```{r output=FALSE, message=FALSE}
# run simulation pipeline
withr::with_dir(here::here("simulation"), {
  tar_make()
  
  tar_load(check_wd)
  tar_load(sim_pairwise)
})

# and from the general
tar_load(variables_tab)


```

```{r}
# check we're in the simulations directory
check_wd
```


Our goal is to create a dataset that imitates the kind of data we will encounter in the cleaned Covidence extract. The cleaning is such a substantial job, I think it useful to simulate a manageable dataset to play around with model subgroups and visualisations. 

Given the number of studies involved, and the number of treatments, it's likely we will need to create several customaised visualisations and summaries. 

Off the top of my head, we have

- time points: follow-ups short and long, post-intervention, 
- comparisons: antidepressant vs placebo, etc.
- `class` of drug
- chronic pain `condition`
- outcome

> ugh sort out type and class, what does the protocol say? 


For now, I will use this table as my guide. 

```{r variables table}
variables_tab
```



## filters

We will assume

- `timepoint` is post intervention
- `scale` filters have not been applied (because Charles need to think about how to code this) 
- `type` of interventions considered are antidepressants vs placebo

So, we will need to add these as columns to the observations. Some outcomes are measured dichotomously and some outcomes are measured continuously. So, for one outcome, for the filters above, we have:

```{r set up basic model input}
n_obs <- 5

# need to create a few set up tables

# scale is associated with drug
drugs <- 
  tibble(
    drug = 1:3,
    scale = sample(1:2, 3, replace = TRUE)
  ) 

study <- 
  tibble(
    study = sample(1:3, )
  )

# 

# study and name of drug
  tibble(
  drug = sample(drugs$drug, n_obs, replace = TRUE)
) %>% 
    left_join(drugs, by = "drug") %>% 
  mutate(
      name = glue("drug_{drug}"),
    row = row_number(),
  study = glue("study_{row}")
  ) %>% 
  select(-drug, -row) %>% 
    mutate(
      timepoint = "post_int",
      type = "antidepressant"
    )
 

```



## model 

### pairwise

In pairwise, we model, for the $i$th study, we assume the observed difference between placebo and intervention $d_i$ can be thought of in terms of some true difference $\delta$ and a random effect $\delta_i \sim \text{normal}(0, \tau)$ associated with the specific conditions of the difference $d_i$ in the $i$th study,

$$
d_i = \delta + \delta_i + \varepsilon_i, 
$$
with $\varepsilon_i \sim \text{normal}(0, \sigma_i^2)$, some sampling error.

So, then

$$
\begin{cases}

d_i \sim \text{normal}(\delta_i, \sigma_i^2)\\
\delta_i \sim \text{normal}(\delta, \tau) 

\end{cases}
$$
(I think, I'm still getting my head around this notation.)


```{r}



```


### network meta-analysis model

One of the questions I'm trying to answer is _which_ model `multinma::` uses. 