---
title: "Covidence"
description: |
  For checking with Hollie and Gav.
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r pkgs}
library(tidyverse)
library(gt)
library(RColorBrewer)

```

## in this document

- model notes from protocol
- QA for model
- model definition

These all have different objectives, but are overlapping. 

# model definition

# QA for model


### keywords

```{r data}
keywords <- read_csv("data-raw/keywords.csv")

```

```{r table}
keywords %>% 
  gt(rowname_col = "keyword", groupname_col = "outcome") %>% 
  data_color(
    columns = vars("inclusion_criterion"),
    colors = scales::col_factor(
      palette = "Blues",
      domain = NULL
    )
  ) %>% 
  tab_header(
    title = "Inclusion criteria",
    subtitle = "Columns including or excluding these words are extracted from the Covid export"
  ) %>% 
  tab_options(
    row_group.background.color =  "steelblue",
    table.background.color = "aliceblue"
  )

```



# protocol notes

## background

We want to assess the comparative efficacy of antidepressants for adults with chronic pain. 

### condition

- **chronic pain** := > 3 months
- **primary pain** := chronic pain as disease, e.g. lower back pain
- **secondary pian** := pain with a specific cause, e.g., osteoarthritis
- assessed by self report
- affects 1/5 of adults in the world
- affects qol, mood, sleep, physical function

### intervention

- different classes of treatment for chemical structure and mechanism of action
- common classes: TCA, SSRI, SNRI, MAOI
- antidepressants are sometimes used 'off-license' to treat chronic pain
- adverse events (e.g., headaches, weight loss) are associated with antidepressants

### how

- antidepressants work by targeting neurotransmitters & receptors associated with mood & emotion
- prevent signal of pain from being absorbed
- perceived pain is reduced

## important

- no nma yet in pain + antidepressants
- contradictory evidence
- no comparison of pain vs mood

## objectives

- assess improvements in pain, mood, pgic, physical function, sleep, and qol by type, class, dose
- adverse events by type, class, dose
- rank efficacy in treating pain, negative affect, and adverse events


