---
title: "Hollie"
description: |
  For exploration
author:
  - name: Hollie and Charles
date: "updated `r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

```{r packages}
# if it says package not installed:
# run renv::restore() in the console to install all packages

library(tidyverse) # vis and wrangling
library(targets) # pipeline
library(gt) # tables

source("R/hpp_themes.R")

```

# Stuff for Hollie to investigate

## studies

Some studies' titles don't match covidence.

```{r}

tar_read()


```


## scales

### unmatched scales

```{r eval=FALSE}
# these are the scales that aren't matching yet
# some have 0 matches some have > 1
# hit the green play button in the right of this chunk to see all
# aka_det matches aka column (not raw), cat_det matches scale_category column

excluded_scales <- 
  tar_read(w_obs_scale_excluded) %>%
select(study, arm, covidence_desc, scale_match) %>% 
  unnest(scale_match) 

# view it in RStudio
excluded_scales %>% 
  # patch in the titles
  left_join(tar_read(w_study_key) %>% mutate(study = tolower(study))) %>%
  select(
    covidence_desc, study, title, contains("aka"), contains("cat"),  everything()
  ) %>% 
  View()

# if you want to export it as a csv, remove the # from the line below and run it
# it will write to exports
# write_csv(excluded_scales, "exports/excluded_scales.csv")

```

### higher direction of improvement

- For direction of improvement `higher` find as many `upper_range` as possible, otherwise these observations will be excluded

```{r eval=FALSE}
# just look at direction of improvement is higher in scales
# AND that upper range check is FALSE
tar_read(w_scales) %>% 
  mutate(upper_range_check = map(upper_range, is.double)) %>%
  filter(direction_of_improvement != "Lower") %>%
  select(direction_of_improvement, upper_range, upper_range_check, everything()) %>% 
  arrange(direction_of_improvement, upper_range_check) %>% 
  View()
  
```

## duplicates

This is for both of us to investigate after we've done all scales and all studies

```{r}
tar_read(w_obs_wide_duplicates) %>% View() 

```

## observations with problematic measurements

```{r}
# these are the problematic measurement  

tar_read(w_obs_investigate) %>% 
  count(outcome, study)

tar_read(w_obs_investigate) %>% View()

```


# Hollie writes here:

This is a test

# Tutorial stuff from Charles

NB: only edit this file

## targets

The pipeline is managed by the `targets::` package. 

A few key commmands.

NB: we've turned off this "code chunk" because it takes ages to render

You can run single lines of code by hitting `cmd + enter` or the whole chunk by clicking the green play button.  

```{r eval = FALSE}
# inspect the pipeline

tar_glimpse()

# inspect a subset of the pipeline

# run specific parts of the pipeline: starts_with *_

# starts_with labels

# r := raw
# w := wrangling
# m := model
# c := check, for exporting checks and asserts
# e := exploratory data analysis table or vis
# p := pipeline design

# secondary signifiers ^_*_

# h := prepared by hollie

# targets that contain
tar_glimpse(allow = contains("_h_"))

# targets that start with
tar_glimpse(allow = starts_with("r_"))

```

Accessing data from targets.

Desired table output of all observations.

outcome | study | arm | observations | observation info | study-level descriptors
- |-|-|-|-|-
outcome label | unique identifier for study | unique identifier for arm | mean, sd, counts, etc. | timepoint, scale, etc.| condition, study design (parallel/crossover), antyhing we need to filter by, subgroups, etc.


```{r}
# inspect the data at a point in the pipeline with 

# this is the output table described as the desired output at the top
# of the pipeline (copied in above)
tar_read(w_obs)

```

## syncing with Charles

NB: Charles is learning, too! 

See [this](https://usethis.r-lib.org/articles/articles/pr-functions.html) page for more details:

```{r eval=FALSE}

# grab latest changes from Charles
pr_merge_main()

# make changes
# commit in the git pane

# send changes to Charles
pr_push()

```

# scales

```{r}
tar_visnetwork(allow = c(contains("scale"), w_obs_long))

tar_read(w_obs_scale_counts)

tar_read(w_obs_scale_snapshot)





```



## investigate unmatched scales

```{r}

# look at the first 0 matches
tar_read(w_obs_scale_counts) %>% 
  filter(cat_n == 0,
         # fix in Covidence bansal 2009 add in 0-4 
         study != "bansal 2009",
         # change kayiran vas 0-10 
         study != "kayiran 2010",
         # change extractions
         !str_detect(covidence_desc, "catastrophising") 
         )

```

## notes

- only need range of scale if direction is higher not lower

## assumptions about scales

- kayiran 2010 lowest is ~1 and highest ~9, so we assumed it is 0-10 vas scale

## changes to make outcome extractions

- [x]  exclude tetreault 2018 catatrosphising columns

## scales to discuss further/investigate

- chest_pain_pain_index_duration_of_chest_pain_weighed_by_the_intensity_of_chest_pain_baseline in spinhoven 2010 
- tetreault 2018 - detect questionnaire scales 

# using `gt::`

`gt::` is an R package for creating tables

- [cookbook](https://themockup.blog/static/gt-cookbook.html#Introduction)
- [pkg site](https://gt.rstudio.com/)

```{r}
# example of using gt

tar_read(w_obs) %>%
  # select first 10 columns
  select(1:5) %>% 
  select(-covidence) %>% 
  # first 10 rows
  head(3) %>% 
  gt() %>% 
  hpp_tab(vertical_divider = "outcome")
  
  
```

