---
title: "Hollie"
description: |
  For exploration
author:
  - name: Hollie
date: "updated `r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}

# if it says package not installed:
# run renv::restore() in the console to install all packages

library(tidyverse) # vis and wrangling
library(targets) # pipeline
library(gt) # tables


```

# Hollie writes here:

This is a test

# Tutorial stuff from Charles

NB: only edit this file

## targets

The pipeline is managed by the `targets::` package. 

A few key commmands.

NB: we've turned off this "code chunk" because it takes ages to render

You can run single lines of code by hitting `cmd + enter` or the whole chunk by clicking the green play button.  

```{r eval = FALSE}
# inspect the pipeline

tar_glimpse()

# inspect a subset of the pipeline

# run specific parts of the pipeline: starts_with *_

# starts_with labels

# r := raw
# w := wrangling
# m := model
# c := check, for exporting checks and asserts
# e := exploratory data analysis table or vis
# p := pipeline design

# secondary signifiers ^_*_

# h := prepared by hollie

# targets that contains
tar_glimpse(allow = contains("_h_"))

# targets that start with
tar_glimpse(allow = starts_with("r_"))

```

Accessing data from targets.

Desired table output of all observations.

outcome | study | arm | observations | observation info | study-level descriptors
- |-|-|-|-|-
outcome label | unique identifier for study | unique identifier for arm | mean, sd, counts, etc. | timepoint, scale, etc.| condition, study design (parallel/crossover), antyhing we need to filter by, subgroups, etc.


```{r}
# inspect the data at a point in the pipeline with 

# this is the output table described as the desired output at the top
# of the pipeline (copied in above)
tar_read(w_obs)

```

## syncing with Charles

NB: Charles is learning, too! 

See [this](https://usethis.r-lib.org/articles/articles/pr-functions.html) page for more details:

```{r eval=FALSE}

# grab latest changes from Charles
pr_merge_main()

# make changes
# commit in the git pane

# send changes to Charles
pr_push()

```



