---
title: "pipeline design"
description: |
  Overview of pipeline from raw data to models.
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r pkgs}
library(tidyverse)
library(targets)
library(gt)

source("R/hpp_themes.R")

```


# objective

Goal is to produce a table in the format:

study | arm | observations | observation info | study-level descriptors
-|-|-|-|-
unique identifier for study | unique identifier for arm | mean, sd, counts, etc. | timepoint, scale, etc.| condition, study design (parallel/crossover), antyhing we need to filter by, subgroups, etc.

Column names need to be interpretable by everyone in the group.

In some cases, there is a column or columns that uniquely identify/provide the required data. In other, more challenging cases, we need to extract information from a substring of the observation header (column header). 

```{r}
tar_read(e_variables)
```

# raw data

```{r}

tar_manifest(names = starts_with("r_"), fields = c(name, command)) %>%
  gt() %>% hpp_tab(vertical_divider = "name")


```


# model input data

Observations are drawn from the raw files provided by Hollie, and study-level information from the raw Covidence export, as well as column headers in the observations. 

To do this we will join by matching the study and arm columns in two tables. 

```{r}
tar_read(p_metapar)

```

With outcome-level observational data:

```{r}
tar_read(p_obs)
```

# model parameters

We'll construct a dataframe to run models over that contains all combinations of unique subgroups we wish to run network meta-analyses over.

Ideally this will be implemented in a shiny app.