---
title: "outcome analysis"
description: |
  Within-outcome analysis 
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
params: 
  outcome: "mood"
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r pkgs}
library(tidyverse)
library(multinma)
library(gt)

```


```{r get model}

```



# nma

We will provide a network meta-analysis (NMA) **for each outcome**, which adheres to Cochrane's MECIR [@higgins2016] standards for reporting network meta-analyses, in particular, this entails ensuring we meet the thirty-two requirements in the extended PRISMA checklist for network meta-analysis [@hutton2015]. 

## parameterised report

This page is a **parameterised report**. Each analysis, for each outcome, requires a number of standardised reporting procedures, that is, tables and visual summaries of statistical results and exploratory data analysis. This page is an automatically-generated report for the outcome producing standardised analyses for a specific outcomes. 

When we get closer to publication, we may wish to do outcome-specific analyses in addition to the standardised analyses presented in the parameterised reports.

This is the automatically-generated parameterised report for the outcome: **`r params$outcome`**.


# structure of analysis

```{r echo=TRUE}
# need table of variables here

```


# simulation parameters

```{r echo=TRUE}
# model parameters: subgroups, etc.
# filter model table

```

# random effects models 

## cipriani-style all-in

## subgroup analyses

### condition [general grouping]

### type [SSRI]

### comparisons 

# pairwise 


