---
title: "wrangling"
description: |
  Data cleaning of observations and study-level information.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r pkgs}
library(tidyverse)
library(targets)
library(gt)

source("R/hpp_themes.R")

```

# study

There's a shorthand tag for study (first author and year) that we'll use for the labelling in the forest plots and joining the different datasets, however, this tag is not unique.

So, the `study` tag appends with a number _if_ there is more than one study by that author in a year. 

```{r}
tar_read(w_study_key) %>% 
  filter(str_detect(study, "Arnold")) %>%
  mutate(title = str_trunc(title, width = 30)) %>% 
  gt() %>% 
  hpp_tab(vertical_divider = "study")
  
```

This function is used to construct a study key, and variables are relabelled in the study-level data extracted from Covidence, and the outcome observations extracted by Hollie. 

```{r}
tar_visnetwork(allow = c(
  starts_with("r_h_"),
  contains("covidence"),
  starts_with("w_study_"),
  contains("outcome")
))

```

We now have two datasets each with `study` and `arm`, so we can join them together later. 

```{r}
# table of study/arm level information
tar_read(w_study_label_study_arm_par)

# list of outcome tables with observations extracted by Hollie
tar_read(w_study_label_obs) %>% 
  # select first 10 columns bc space
  map(select, c(1:10))

```

# study-level information 




# observations and observation-level information

```{r}
# desired output structure

tar_read(p_obs)

# pipeline overview

tar_visnetwork(allow = c(w_study_label_obs, starts_with("w_obs_")))

```

Before we identify timepoints and other observation-level variables, we check that the data are in the correct format. The `measure_desc` column is the orgiinal column header from Covidence prefix for the measure. We'll extract the observation-level variables (timepoint and scale) from this column.

```{r}
tar_read(w_obs_wide)

```

## timepoints

We are interested in classifying timepoints as post-intervention, short-term follow up, and long-term follow up. 

```{r}
# get counts for timepoints, particularly interested in checking there are no unmatched timepoints
tar_read(w_obs_time) %>% 
  count(timepoint)

```

## scales

```{r}

```

