---
title: "models to answer questions"
subtitle: "in what terms might we think of the observed effects?"
# description: |
#   Statistical methods for answering questions in the protocol.
# author:
#   - name: Nora Jones 
#     url: https://example.com/norajones
#     affiliation: Spacely Sprockets
#     affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
# output: distill::distill_article
output: 
  ioslides_presentation:
    widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r packages}
library(tidyverse)
library(gt)
```


```{r targets}
withr::with_dir(
  here::here(), {
    tar_load(w_obs)
    
    source("R/hpp_themes.R")
  }
)


```

## in terms of {.smaller} 

### How we might we think of an **outcome** associated with pain in terms of **condition**, **class** of antidepressant, **antidepressant**, **dosage**? 

**outcome**: `r w_obs %>% pull(outcome) %>% unique()` ... [or]

[_and_?]

### in terms of 

**condition**: `r w_obs %>% pull(condition_general) %>% unique() %>% head()` ... 

**class**: `r w_obs %>% filter(str_length(class) > 2) %>% pull(class) %>% unique()`

**antidepressant** `r w_obs %>% pull(intervention) %>% unique() %>% head()` ...

**dosage**: `r w_obs %>% pull(arm) %>% unique() %>% head()` ... 

## network meta-analysis | on subgroups

For each **outcome**, **condition**, and **class**, we can run a separate nma that asks: how well does the treatment work compared to placebo?

That is we can estimate:  

outcome = placebo + intervention

for each condition and class. 

[NB: Charles is confident with this]

[Next approach is a work in progress]


## network meta-analysis | is _fancy_ but still just **regression to the mean** {.smaller}

We assume we can think of an outcome in terms of adding _in terms of_ together.

Network meta-analysis assumes each observation has some error associated with the **study**, **intervention**, and **sampling** to produce an estimate _in terms of_:

### how might we define _in terms of_?  "average" estimates + together

outcome = placebo + intervention

outcome = placebo + class + class (intervention)

outcome = placebo + condition + class (condition) + class (condition, intervention)

outcome = placebo + condition + class (condition) + class(condition, intervention) + class(condition, intervention, dosage)

[Charles knows how to do this in MA but is still learning in NMA.] 


## in terms of | outcome = placebo + intervention

```{r}
outcome_obs <- 
  w_obs %>% 
  filter(outcome == "mood_depression")

classes <- 
  outcome_obs %>%
  filter(intervention != "placebo") %>% 
  select(class, intervention) %>% 
  distinct()

interventions <- 
  classes %>% 
  pull(intervention) %>% 
  unique()

```

Let's make some numbers up! 

Assume mood is reported on a numerical rating scale of 0 to 10.

```{r}
tibble(
  outcome = rep("mood", 3),
  placebo = rep(6, 3),
  intervention_effect = c(0, -4, -3)
) %>%
  mutate(
    intervention = c(NA, interventions[1:2]),
    outcome_effect = placebo + intervention_effect
  ) %>% 
  select(contains("outcome"), placebo, contains("intervention")) %>% 
  gt() %>% 
  hpp_tab(vertical_divider = "outcome_effect")


```


## in terms of | outcome = placebo + class + class (intervention)

```{r}
tibble(
  class = NA,
  intervention = "placebo",
) %>% 
bind_rows(classes[c(1:2, 6), ]) %>% 
  mutate(
    outcome = rep("mood", 4),
      placebo = rep(6, 4),
    class_effect = c(0, -1, rep(-2, 2)),
    intervention_effect = c(0, -1, -2, -3),
    outcome_effect = placebo + class_effect + intervention_effect
  )  %>% 
    select(contains("outcome"), placebo, contains("class"), contains("intervention")) %>%
  relocate(class_effect, .before = class) %>% 
  relocate(intervention_effect, .before = intervention) %>% 
  gt() %>% 
  hpp_tab(vertical_divider = "outcome_effect")

```

## nma | Making sense of it all

Presumably network meta-analysis is really just a random-effects model. 

For a meta-analysis to run we need estimates of each effect. 

However, in NMA some observations are missing. 

So, if the models are too complex (or annoying) to work in `multinma::` 

1. Estimate effects
2. Construct model 
