---
title: "data cleaning pipeline"
description: |
  Documentation of how data is cleaned and prepared.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



```

```{r pkgs, message=FALSE}

library(targets)
library(tidyverse)
library(gt)
library(glue)

source("R/hpp_themes.R")

```

In this document, I'll step through how the data was labelled so Hollie and others can check the assumptions and labelling.

```{r}
# overview of entire pipeline

tar_visnetwork()
```

We need to ensure that the following variables and filteres are labelled and indexed correctly for the models. 

```{r warning=FALSE}
tar_read(e_variables)
```


# raw data

The inputs to the analysis are from a number of different raw data files.

```{r}
tar_visnetwork(allow = starts_with("r_"))
```

# raw outcome-level data

Hollie identified the columns in the raw Covidence export that pertained to each outcome and exported them as a separate .csv file. These were loaded into a list of dataframes to be fed into the pipeline for cleaning.

In theory, the pipeline is built such that new outcome-level observations can be dropped in.

```{r}
# pipeline of raw observations

tar_visnetwork(allow = starts_with("r_outcome_"))
```

## other raw inputs

# studies

The current dimensions of the covidence export are

```{r dim cov}
tar_read(r_covidence) %>% 
  dim()
```

where each row denotes an arm of a study and the columns are sparsely-filled observational data, as well as study-level information. As we have the observational data from Hollie's extractions for each outcome, these data are only used for study-level information. 

Number of studies in raw covidence , for comparison with cleaned observations.

```{r studies in cov}
tar_read(r_covidence) %>% 
  janitor::clean_names() %>% 
  select(study_identifier, comments) %>% 
  distinct() %>% 
  nrow()


```

Some of the studies have the same label (first author and year), as the first author published more than one study in a year. 

```{r}
tar_read(r_covidence) %>% 
  janitor::clean_names() %>% 
  select(study_identifier, comments) %>% 
  distinct() %>% 
  group_by(study_identifier) %>% 
  mutate(n_per_author = 1:n(),
         max_n = max(n_per_author)) %>% 
  filter(max_n > 1) %>% 
  ungroup() %>% 
  gt() %>% 
  hpp_tab(vertical_divider = "study_identifier")


```

For short-hand labelling on the forest plots, we append a number to the author-year shorthand study identifier. 

```{r}
source("R/study_id.R")

tibble(
  study_identifier = c(rep("birkinshaw 2019", 3), "gray 2014", "pincus 2018"),
  title = letters[1:5]
) %>% 
  study_id()

```




## study-level data

Metaparameters for each study were drawn from the raw covidence export. These comprise the study and intervention data, such as class, type of trial, etc.

```{r}
tar_read(metapar) %>% gt()

```

## outcome data

```{r}
tar_read(r_obs) %>% map(select, 1:5)
```

# wrangling

```{r}
tar_visnetwork(allow = starts_with("w_"))
```
