---
title: "access"
description: |
  for researchers' internal use
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This site is intended for internal use in team meetings.

Instructions for the team to access the analysis. Don't hesitate to ask Charles for assistance. 

## raw data

Hollie and I haven't posted the raw data yet; email Charles to request access to current raw data.

## rstudio users

You can access past and present analyses, visualisations, datasets, etc. using a combination of `renv::` and `targets::`. 

Here are the instructions. 

### get the analysis

Two options: easy and hard. Alas, there is no in between. 

Easy is fine for one-time investigation. However code contributions (may well be unlikely) or frequent inspection (Hollie might like this) may be facillitated by the hard option. 

1. Easy: download for one-time inspection by [clicking the green code button and downloading zip](https://github.com/softloud/happypillpain).
2. Hard: The [`usethis::` pull request method](https://usethis.r-lib.org/articles/articles/pr-functions.html. Note that this assumes RStudio has been configured for interfacing with GitHub; an annoying step, expect it to take a couple of hours. 

### get the data

For everyone's peace of mind, we're not pushing the data to an open source repository until publication. 

For now, Charles will email you a directory **data/** which you should unzip and copy into **happypillpain/**. So that it now exists as the directory **happypillpain/data/**.

### get the tools

We'll install the `renv::` package that will match up the correct version of all the packages.

```{r eval=FALSE, echo=TRUE}

# install renv
install.packages("renv")

# update packages
renv::restore()

```

### inspect the analysis 

We use the package `targets::` to inspect the analysis.

```{r echo=TRUE}
library(targets)




```

```{r}
# see all the objects produced in the analysis workflow and how they feed into each other
tar_glimpse()

# see what's working and not working in the piepline
tar_visnetwork()


```

```{r}
# inspect an element called metapar
tar_read(metapar)

# inspect an element called variables_tab
tar_read(variables_tab)



```

```{r eval=FALSE}

# load metapar into the environment
tar_load(metapar)


```

